\documentclass[margin]{res}
\setlength{\textwidth}{5.1in}
\setlength{\textheight}{8.5in}

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Julio Capote}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{www.juliocapote.com}
\moveleft.5\hoffset\centerline{www.github.com/capotej}
\moveleft.5\hoffset\centerline{jcapote@gmail.com}

\begin{resume}

  \section{SUMMARY} Agile Ruby Web Developer/UNIX Administrator
  with 8 years experience implementing, deploying, and administering large
  software systems using various technologies. Specializes in modernizing
  legacy applications, distributed/cloud computing, and web service interaction.


  \section{SKILLS}
  {\sl Languages:} \/ Ruby, Javascript/Coffeescript, Java/Scala(lite), Erlang(lite)  \\ \\
  {\sl Databases:} \/ Redis, Riak, Solr, MySQL  \\ \\
  {\sl Frameworks:} \/ Rails 2 \& 3, Sinatra, Eventmachine, Backbone \\ \\

  \section{EXPERIENCE} 

  {\sl Software Engineer } \hfill 2011-Present \\
  Posterous.com, San Francisco, CA
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Created ``Posterous-in-a-Box'', a self-contained version of Posterous running all required services on EC2. This system enabled rapid creation of new development environments for all engineers.
    \item Set up a spam defense system that would analyze uploaded videos, automatically banning pirated and copyrighted content and controlling abusive behavior on service.
    \item Assisted in migrating our codebase to Bundler.
    \item Deployed a customized StatsD instance for realtime monitoring of performance metrics across the site.
    \item Wrote a service that automatically retasked the asynchronous job infrastructure according to demand.
    \item Implemented an API rate limiter with per-user quotas and a token whitelist.
    \item Optimized and tuned our Rails/Solr integration to achieve near real-time search.
    \item Profiled and tweaked the Ruby garbage collector for improved performance.

  \end{itemize}

  {\sl Lead Developer } \hfill 2009-2011 \\
  Destructoid.com, San Francisco, CA
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Led an initiative to port three legacy PHP codebases into a single multisite Rails framework.
    \item Used Redis and Varnish to intelligently cache a contextually specific, highly dynamic website to thousands of concurrent users.
    \item Wrote an event-driven upload server in Ruby (using Eventmachine/Rainbows) to handle multiple concurrent uploads (http://github.com/capotej/uploadd).
    \item Deployed and scaled a high traffic Rails site using EngineYard and Heroku.
    \item Patched and customized dozens of popular open source gems/plugins for performance and scaling.
  \end{itemize}


  {\sl Founder/Developer } \hfill 2007-2009 \\
  Nuklei.com, Miami, FL
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Architected a distributed, end-to-end supply chain management system that synchronized orders
      and inventory across distributors and marketplaces.
    \item Created a multi-threaded Java web application that converted PDFs into
      universally accessible javascript slideshows for a local newspaper.
    \item Implemented ``upload-by-email'' functionality for various websites, giving clients the ability to easily
      update their website via email.
    \item Advised clients on best practices and speed/traffic optimizations for their web sites.

  \end{itemize}

  {\sl Web Developer} \hfill 2006-2007 \\
  Worldmedia, Miami, FL
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Implemented a solution that backed up important sites/databases
      to an off-site server for safekeeping.
    \item Setup and administrated several mission critical, load-balancing
      environments for heavily loaded sites (800,000+ page views a day).
  \end{itemize}

  {\sl Systems Engineer} \hfill            2003-2006 \\
  Computer Science Department, FIU, Miami, FL
  \begin{itemize}  \itemsep -2pt %reduce space between items
    \item Created a monitoring system for all of our hosts/servers, which allowed
      for higher availability and faster response times.
    \item Founded Madlab, an organization/club geared towards teaching UNIX/
      Linux concepts to peers from a hands-on perspective
    \item Managed a heterogeneous Windows and Linux environment (Windows and UNIX) with
      custom tools written for both platforms.
  \end{itemize} 

\end{resume}
\end{document}
